Assignment 03
=====

### Load the juul data in the ISwR package.

```{r}
library(ISwR)
library(ggplot2)
```

### Plot a histogram of IGF-1

```{r}
qplot(igf1, data = juul)
```

### Determine the SEM for IGF-1 between males and females in the sample.

```{r}
m.m <- with(juul, mean(igf1[sex == 1], na.rm = TRUE))
m.f <- with(juul, mean(igf1[sex == 2], na.rm = TRUE))
n.m <- with(juul, length(igf1[sex == 1]))
n.f <- with(juul, length(igf1[sex == 2]))
v.m <- with(juul, var(igf1[sex == 1], na.rm = TRUE))
v.f <- with(juul, var(igf1[sex == 2], na.rm = TRUE))

m.sem <- sqrt(v.m/n.m)
f.sem <- sqrt(v.f/n.f)
m.sem
f.sem
```

### Calculate The 95% confidence interval around difference in IGF-1 for this sample. Does the observed difference fall inside this CI?

```{r}
m.m-m.f
sem <- sqrt(v.m/n.m + v.f/n.f)
0 + c(-2, 2) * sem

# also

(m.m - m.f) + c(-2, 2) * sem
```

The observed difference of `r m.m-m.f` falls well outside the interval `r 0 + c(-2, 2) * sem`, suggesting that males and females differ in terms of IGF-1 concentration.