Assignment 5
======

1. Load the ChickWeight dataset
2. Model weight as a function of Time and Diet.
3. Explain the coefficients, recommend whether you think Time or Diet predicts weight.
4. Create a plot or series of plots to go along with this model. Does the plot suggest that you might be missing something in your model?

```{r}
library(arm)
data(ChickWeight)
fit <- lm(weight ~ Time + Diet, data = ChickWeight)
display(fit)
```

If we predict weight as independently predicted by Time and Diet, we would predict an increase of about 9 on our outcome for each unit increase in time. We would also infer that we predict diets 2, 3, and 4 to produce higher weights than diet 1, (because the coefficients for those diets are more than twice the coefficient SE and diet 1 is our baseline). If we examine a plot of the data, however, we can see that weight seems to change over time differently with each diet.

```{r}
library(ggplot2)
ggplot(ChickWeight, aes(x = Time, y = weight, color = Diet)) + geom_point() + geom_smooth(method = "lm", se = FALSE)
# Equivalently:
# qplot(Time, weight, data = ChickWeight, color = Diet, geom = c("point", "smooth"), se = FALSE, method = "lm")
```

This would be captured by including an interaction between Time and Diet in our model, which improves the fit of our model.

```{r}
fit2 <- lm(weight ~ Time + Diet + Time:Diet, data = ChickWeight)
AIC(fit)
AIC(fit2)
```