Lab 7
=====

1. Use the R.matlab package to load permExData.mat
2. These data load as a list including two variables. Munge the data into a data.frame in which one column reflects the values in two vectors in the original list and another column reflects which list the data came from.
3. Plot a histogram of the data. Pay specific attention to binwidth. Can you see evidence that these are latencies measured in hours?
4. Perform a t test. Does latency differ between the groups?
5. These data are strongly non-gaussian. Perform a permutation test. Does your inference change?

```{r,warning=FALSE,message=FALSE}
library(R.matlab)
library(reshape2)
library(ggplot2)
dat <- readMat("~/Dropbox/statistics/students/labs/permExData.mat")
df <- melt(dat)
df$L1 <- factor(df$L1)
qplot(value, data = df, binwidth = .5) + ylim(c(0, 100))
```

```
With a small binwidth, especially when limiting the extent of the y-axis, it is easy to see periodicity in the data such that measurements are centered on 24-hour intervals.
```

```{r}
t.out <- t.test(value ~ L1, data = df)
t.out
```

```
The latency does not differ between groups, though the t-value is quite high.
```

```{r}
permTest <- function(df) {
  df$L1 <- sample(df$L1)
  return(t.test(value ~ L1, data = df)$statistic)
}
t.null <- replicate(10000, permTest(df))
sum(abs(t.null) > abs(t.out$statistic))/10000
```

```
With sufficient samples, the permutation test shows that the probability of observing a larger value by chance is less than .05, suggesting a difference in group means.
```