Lab 11
=====

```{r}
library(rstan)
l_mod <- '
parameters {
  real mu;
}
model {
  mu ~ normal(0, 1);
}
'
fit <- stan(model_code = l_mod)
```

1. Describe the function of the preceding code.
2. How could you replicate this functionality using functions in R?
3. Attempt to generate a posterior distribution for some arbitrary prior and a normal likelihood function with the following observations: 45, 18, 23, 1, 19.

Question 1
-----

That code asks stan to sample a single parameter, $\mu$, from a normal distribution with a mean of 0 and a variance of 1

Question 2
-----

```{r,eval=FALSE}
out <- rnorm(1000)
```

Question 3
-----

The following code generates a posterior distribution for the mean and variance of the population normal distribution conditioned on our priors and our data.
In this model, our data are comprised of the five samples we "sampled."
We have chosen a relatively uninformed prior for our $\mu$ parameter - we say that it can only vary between the extreme possible scores of the test 0 and 100, but that all means in that range are equally likely.
We specified a prior for our $\sigma$ parameter that suggests large variances are unlikely.
This will give us a narrower estimate of the mean than a less-informed prior, but could also make us overconfident about the $\mu$ parameter.

```{r}

library(rstan)
mod_code <- '
data {
  int<lower=0> N;
  vector[N] y;
}
parameters {
  real mu;
  real<lower=0> sigma;
}
model {
  y ~ normal(mu, sigma);
  mu ~ uniform(0, 100);
  sigma ~ exponential(1.0/1000.0);
}
'

mod_dat <- list(y = c(45, 18, 23, 1, 19), N = 5)

fit <- stan(model_code = mod_code, data = mod_dat)
fit
```